---
title: "Quantifying the Visual Mechanisms Underlying the Rod-and-Frame Illusion"
author: "Ernestine Brannon"
output:
  html_document:
    code_folding: hide
    fig_width: 6
    fig_height: 4
  pdf_document: default
  word_document: default
---
```{r setup, include = FALSE, echo= FALSE}

#rm(list=ls())
library(here)
library(knitr)
library(tidyverse)
library(rstatix)
library(gridExtra)
library(rempsyc)
library(psych)
library(ggstatsplot)
library(papaja)
pkgs <- c("effectsize", "flextable", "broom", "report")
install_if_not_installed(pkgs)
library(effectsize)
library(flextable)
library(broom)
library(report)
library(doBy)
library(RColorBrewer)
library(ggpubr)
library(ggsignif)
library(GGally)
library(kableExtra)
library(flextable)
library(modelsummary)


f_x <- 960 #fixation point x value

f_y <-  850 # fixation point y value
```

## Analysis {.tabset}


```{r load perception data as p_data_raw, include=FALSE, echo=FALSE}

optimized_df_file<- here("data","optimized_parameters.csv")
optimized_df<- read.csv(optimized_df_file)
optimized_df$sid<-gsub("RFT_Sizes_Perception","",optimized_df$sid)

#Load perceptual data

data_dir_p <- here("data","p_results")

sids_p<- list.files(data_dir_p) #subject IDS

p_data_raw<- NULL #empty variable that will be filled through the for loop below

#Bind together all the data across subjects
for (i in seq_along(sids_p)) {
  
  fname <- list.files(file.path(data_dir_p, sids_p[i]), 
                      pattern = "RESULTS_FILE")#, full.names = TRUE)
  
  p_tmp_data <- rio::import(paste0(data_dir_p,"/", sids_p[i]), na.strings = c("NULL"))
  
  p_tmp_data$sid <- sids_p[i]
  
  p_data_raw <- rbind(p_data_raw, p_tmp_data) #has all of data across subjects
  
}


```

```{r clean perceptual data, include=FALSE, echo=FALSE}
p_data_clean <- p_data_raw %>%
  janitor::clean_names() %>%
  filter(trial_type == "real",
         !is.na(response),
         rt <= 4000) %>% 
  select(sid, everything()) %>% 
  arrange(sid, trial_number) %>%
  mutate( # add useful columns
    # recode frame tilt 
    frame_orient = ifelse(frame_tilt == "-15", "Left", "Right"),
    # recode staircase approach
    stair_approach = ifelse(stringi::stri_sub(trial_variant, -1) == "L", "Left", "Right"))%>%
  # Parse image name
  #frame_175_15.png
    mutate(image_name2 = str_remove(frame_name,"frame"))%>%
  separate(image_name2, into = c("drop1", "frame_size"), sep = "_|.p") %>% 
  select(-drop1)

p_sids <- unique(p_data_clean$sid)  # list of participant IDs

```

```{r individual RFI magnitude, include=FALSE,echo=FALSE}

# To determine the change in PSE as a function of frame size, we subtracted the PSE for counterclockwise trials from clockwise trials, and then divided that by half. A positive value indicates that participants PSEs are being biased in the direction of the tilt of the frame. 


perception<- optimized_df %>% 
  group_by(sid,frame_size,frame_orientation) %>% 
  summarize(m_pse = -mean(pse)) %>% 
  mutate(frame_orientation=recode(frame_orientation, 'Right'='ccw', 'Left'='cw')) %>% 
  select(sid, frame_size, frame_orientation, m_pse) %>% 
  ungroup() %>% 
  group_by(frame_size, frame_orientation) %>% 
  pivot_wider(names_from = frame_orientation, values_from = m_pse) %>% 
  mutate(frame_effect_perception= (cw-ccw)/2)

perception$frame_size<-as.factor(perception$frame_size)

```

```{r load vertical data as v_data, include=FALSE, echo=FALSE}
#Load vertical data
data_dir_v <-here("data", "v_results")


sids_v<- list.files(data_dir_v) #subject IDS

v_data_raw<- NULL #empty variable that will be filled through the for loop below

#Bind together all the data across subjects
for (i in seq_along(sids_v)) {
  
  fname <- list.files(file.path(data_dir_v, sids_v[i]), 
                      pattern = "RESULTS_FILE")#, full.names = TRUE)
  
  v_tmp_data <- rio::import(paste0(data_dir_v,"/", sids_v[i]), na.strings = c("NULL"))
  
  v_tmp_data$sid <- sids_v[i]
  
  v_data_raw <- rbind(v_data_raw, v_tmp_data) #has all of data across subjects
  
}

v_data<-v_data_raw %>% 
  filter(TRIAL_OUTCOME=="good") # only use valid trials

v_data$sid <- substr(v_data$sid, start = 1, stop = 8) #clean subject ids
#get rid of random extra 

```

```{r calculate v error, echo=FALSE,include=FALSE}
#Performance on each trial was assessed as the difference between true vertical and the angle of rotation of a vector plotted from the fixation point to the final eye position on the response circle. 

f_x <- 960 #fixation point x value

f_y <-  850 # fixation point y value

#Add columns saccade error x and y as sacc_v_error_y and sacc_y_error_x
v_data_calc<- v_data %>%
  mutate(
    sacc_v_error_y = f_y - EYE_Y, #fixationY-saccadeY
    sacc_v_error_x = EYE_X - f_x, #saccadeX-fix
    v_error_radians = atan2(sacc_v_error_x,sacc_v_error_y), #returns angle in radians for tangent y/x,
    v_error = v_error_radians *(180/pi)   #multiply by 180 then divide by pi to get degrees
    
  )

# 
# sanity<- v_data_calc %>% 
#   select(
#     v_error,v_error_radians,
#     EYE_X
#   ) #check 

```

```{r calculate saccade to vertical errors, include=FALSE, echo=FALSE}
#Add columns saccade error x and y as sacc_v_error_y and sacc_y_error_x
v_data_calc<- v_data %>%
  mutate(
    sacc_v_error_y = f_y - EYE_Y, #fixationY-saccadeY
    sacc_v_error_x = EYE_X - f_x, #saccadeX-fix
    v_error_radians = atan2(sacc_v_error_x,sacc_v_error_y), #returns angle in radians for tangent y/x,
    v_error = v_error_radians *(180/pi)   #multiply by 180 then divide by pi to get degrees 
  )
```

```{r v magnitude for each frame size/tilt ,include=FALSE,echo=FALSE}

#The effect of the frames was quantified by subtracting the mean errors for the counterclockwise-tilted frames from those of the clockwise-tilted frames then halving this value to get a measure of the average effect of a single frame (negative values indicated eye movements that deviated in the direction opposite the tilt of the frame).

saccade_to_vert_magnitude<-v_data_calc %>% 
  group_by(sid,FRAME_SIZE_VAL, FRAME_TILT_VAL) %>% 
  summarize(m_errors = mean(v_error)) %>% #The magnitude of the errors were averaged across trials for each of frame tilt/ size and  averaged across rod tilts 
  mutate(FRAME_TILT_VAL=recode(FRAME_TILT_VAL, '-15'='ccw', '15'='cw')) %>% 
  select(sid, FRAME_SIZE_VAL,FRAME_TILT_VAL, m_errors) %>% 
  ungroup() %>% 
  group_by(FRAME_SIZE_VAL,FRAME_TILT_VAL) %>% 
  pivot_wider(names_from = FRAME_TILT_VAL, values_from = m_errors) %>% 
  mutate(frame_effect_v= (cw-ccw)/2)

saccade_to_vert_magnitude$FRAME_SIZE_VAL<-as.factor(saccade_to_vert_magnitude$FRAME_SIZE_VAL)
```

```{r load and clean rod data as r_data, include=FALSE, echo=FALSE}
#Load rod data
data_dir_r <- here("data", "r_results")


sids_r<- list.files(data_dir_r) #subject IDS

r_data_raw<- NULL #empty variable that will be filled through the for loop below

#Bind together all the data across subjects
for (i in seq_along(sids_r)) {
  
  fname <- list.files(file.path(data_dir_r, sids_r[i]), 
                      pattern = "RESULTS_FILE")#, full.names = TRUE)
  
  r_tmp_data <- rio::import(paste0(data_dir_r,"/", sids_r[i]), na.strings = c("NULL"))
  
  r_tmp_data$sid <- sids_r[i]
  
  r_data_raw <- rbind(r_data_raw, r_tmp_data) #has all of data across subjects
  
}

r_data <- r_data_raw %>% 
  filter(TRIAL_OUTCOME=="good") %>% 
    # Parse image name
  #z_long_rod_5.jpg
  mutate(rod_tiltjpg = str_remove(ROD_VAL,"z_long_rod_"))%>%
  mutate(rod_tilt = str_remove(rod_tiltjpg,".jpg")) %>% 
  select(-rod_tiltjpg)

r_data$rod_tilt<-as.numeric(r_data$rod_tilt)


r_data$sid <- substr(r_data$sid, start = 1, stop = 8)
```

```{r calculate r errors, include=FALSE, echo=FALSE}

#Difference between the rod’s actual orientation and the rotation of a vector plotted from the fixation point to final eye position on the response circle.

r_data_calc<- r_data %>% 
  mutate(
    sacc_r_y = f_y - EYE_Y, 
    sacc_r_x = EYE_X - f_x,
    r_saccade = atan2(sacc_r_x,sacc_r_y)*180/pi,
    r_error = r_saccade - rod_tilt
    
  )

```

```{r r magnitude for each frame size/tilt and rod tilt,include=FALSE,echo=FALSE}
#

saccade_to_rod_magnitude<-r_data_calc %>% 
  group_by(sid,FRAME_SIZE_VAL, FRAME_TILT_VAL) %>% 
  summarize(m_errors = mean(r_error)) %>% #The magnitude of the errors were averaged across trials for each of frame tilt/ size and  averaged across rod tilts 
  mutate(FRAME_TILT_VAL=recode(FRAME_TILT_VAL, '-15'='ccw', '15'='cw')) %>% 
  select(sid, FRAME_SIZE_VAL,FRAME_TILT_VAL, m_errors) %>% 
  ungroup() %>% 
  group_by(FRAME_SIZE_VAL,FRAME_TILT_VAL) %>% 
  pivot_wider(names_from = FRAME_TILT_VAL, values_from = m_errors) %>% 
  mutate(frame_effect_r= (cw-ccw)/2)

saccade_to_rod_magnitude$FRAME_SIZE_VAL<-as.factor(saccade_to_rod_magnitude$FRAME_SIZE_VAL)

```

```{r create df with all tasks magnitudes, include=FALSE, echo=FALSE}

################get needed Perception columns

#create a data frame with the illusion magnitude for each task containing just magnitude, sid, frame size
perception_abs<- perception %>% 
  select(sid,frame_size,frame_effect_perception) %>% 
# make sure column names are correct (sid, frame_size, magnitude)
   rename(magnitude = frame_effect_perception) %>%
# # add task column, fill all rows with perception
     mutate(task = "perception") %>% 
# #subtract first character from sid
   mutate(across(c('sid'), substr, 2, nchar(sid))) %>% 
   mutate(frame_size = recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large'))

# make magnitude is positive 
#perception_abs$magnitude<- -1*(perception_abs$magnitude)


################get needed saccade to vertical columns

#create a data frame with the illusion magnitude for each task containing just magnitude, sid, frame size
s2v_abs<- saccade_to_vert_magnitude %>% 
  select(sid, FRAME_SIZE_VAL,frame_effect_v) %>% 
  rename(frame_size = FRAME_SIZE_VAL) %>%
# add task column, fill all rows with perception
    mutate(task = "s2v") %>% 
#subtract first character from sid
  mutate(across(c('sid'), substr, 2, nchar(sid)))


################get needed saccade to rod columns

#create a data frame with the illusion magnitude for each task containing just magnitude, sid, frame size
s2r_abs<- saccade_to_rod_magnitude %>% 
  select(sid, FRAME_SIZE_VAL,frame_effect_r) %>% 
  rename(sub_1 = FRAME_SIZE_VAL, sub_2 = sid) %>% 
  ungroup()


#add the magnitude of the saccade tasks together
saccade_combined<- cbind(s2r_abs,s2v_abs)
saccade_combined$frame_effect_r<- -1*(saccade_combined$frame_effect_r)

saccade_combined$task<- "combined_saccade"

saccade_combined<- saccade_combined %>% 
  select(sid, frame_size, frame_effect_r, frame_effect_v, task) %>% 
  mutate(magnitude = frame_effect_r+frame_effect_v )%>% 
  select(sid, frame_size, magnitude,task) %>% 
  mutate(frame_size = recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large'))


#join by sid
perc_x_sacc_df <- rbind(perception_abs,saccade_combined)

#make sure task and frame size are factors
perc_x_sacc_df$task<- as.factor(perc_x_sacc_df$task)
perc_x_sacc_df$sid<- as.factor(perc_x_sacc_df$sid)
perc_x_sacc_df$frame_size<- as.factor(perc_x_sacc_df$frame_size)

```

```{r create df with all tasks}
all_task<- cbind(s2r_abs,s2v_abs) %>% 
  select(sid, frame_effect_r, frame_effect_v, frame_size)


p_df<- perception_abs %>%
  ungroup() %>% 
  select(magnitude, sid) %>% 
  rename(sub_1 =sid)

all_task<- cbind(all_task,p_df)

all_task<- all_task %>% 
  select(-sub_1)

all_task<-all_task %>% 
  rename(vv= frame_effect_v,
         oc = frame_effect_r,
         perc = magnitude)

across_frames<- perc_x_sacc_df %>%
  pivot_wider(names_from = task, values_from = magnitude)

```


### Perception Task: RFI

To determine the change in PSE as a function of frame size, we subtracted the PSE for counterclockwise trials from clockwise trials, and then divided that by half. 

~~A negative value indicates that participants PSEs are being biased in the opposite direction of the tilt of the frame.~~

```{r percept summary stat table, echo=FALSE}
p_descriptives <- perception %>% group_by(frame_size) %>%
#  mutate(frame_effect_perception = -1*frame_effect_perception) %>% ## the RFI is multiplied by -1
  summarize(
    Mean = mean(frame_effect_perception)
    , Median = median(frame_effect_perception)
    , SD = sd(frame_effect_perception)
    , Min = min(frame_effect_perception)
    , Max = max(frame_effect_perception)
  ) %>% 
  mutate(frame_size = recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

p_descriptives <- p_descriptives %>% 
  rename("Frame Size"= frame_size)
  
#p_descriptives[, -1] <- printnum(p_descriptives[, -1])

desc_perc<-apa_table(
  p_descriptives
  , caption = "Perception Task"
  , escape = TRUE,
  added_stub_head = "Frame Size"
)
#names(desc_perc)[1]<- "Frame Size"

desc_perc
```

```{r mean and sd perc effect, echo=FALSE, include=FALSE}
#t.test.results<- nice_t_test(data= perception_summary_by_frame,  "m_pse")

individual_perc_df <-optimized_df %>%
  select(sid, frame_size, frame_orientation, pse) %>% 
  pivot_wider(names_from = c(frame_orientation,frame_size), values_from = pse) %>% 
  mutate(
    rfi_175 = Right_175 - Left_175,
    rfi_410 = Right_410 - Left_410,
    rfi_645 = Right_645 - Left_645,
    rfi_880 = Right_880 - Left_880) 
  
rfi_summary<- individual_perc_df %>%  
  select(sid,rfi_175,rfi_410,rfi_645,rfi_880) %>% 
  summarize( mean_175 = mean(rfi_175),
  sd_175 = sd(rfi_175),
  mean_410 = mean(rfi_410),
  sd_410 = sd(rfi_410),
  mean_645 = mean (rfi_645),
  mean_880 = mean(rfi_880),
  sd_880 = sd(rfi_880)
  )

#Create table to display means and standard deviations for illusion magnitude (effect of frame size on PSE)

rfi_summary_table<-nice_table(rfi_summary)
rfi_summary_table
rfi_175_ttest<-t.test(individual_perc_df$rfi_175)
report::report(rfi_175_ttest)
rfi_410_ttest<-t.test(individual_perc_df$rfi_410)
report::report(rfi_410_ttest)
rfi_645_ttest<-t.test(individual_perc_df$rfi_645)
report::report(rfi_645_ttest)
rfi_880_ttest<-t.test(individual_perc_df$rfi_880)
report::report(rfi_880_ttest)

```

```{r perc ttest against zero, echo=FALSE}
p_df<-perception%>% group_by(frame_size) %>% do(tidy(t.test(.$frame_effect_perception)))
perc_ttest_table<-nice_table(p_df,
                            title= "Perception Task: RFI")
perc_ttest_table
```


```{r perc aov frame size effect}
p_mag_anova<- aov(frame_effect_r ~FRAME_SIZE_VAL, data =saccade_to_rod_magnitude)
summary(p_mag_anova)
tukey_p<-tukey_hsd(p_mag_anova)
tukey_p
apa_table(tukey_p)
```

***The results between the table and graph are inconsistent due to different tests being used. I am unsure whether I need to use the Tukey HSD test ( shown in the table above) or if a Holm-Bonferroni correction is more appropriate (used in the violin graph below).***

```{r percept repeated measures graph, echo=FALSE}
set.seed(1)
perception<- perception %>% 
  ungroup() %>% 
  mutate(magnitude = frame_effect_perception)%>% 
  mutate(frame_size = recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

p_mag<-ggwithinstats(
  data = perception,
  x = frame_size,
  y = magnitude,
  type = "parametric",
  xlab = "Frame Size",
  ylab = "Perceptual Effect",
  bf.message = FALSE,
  results.subtitle = FALSE,
  centrality.path = TRUE,
  centrality.label.args = list(size = 0,
  segment.linetype = 0, alpha = 0),
  ggsignif.args = list(textsize = 0))

gginnards::delete_layers(p_mag, "GeomText")

#gginnards::delete_layers(p_mag, "StatSummary")


```

### Saccade-to-Vertical Task: Visuovestibular Effect


The effect of the frames was quantified by subtracting the mean errors for the counterclockwise-tilted frames from those of the clockwise-tilted frames then halving this value to get a measure of the average effect of a single frame (negative values indicated eye movements that deviated in the direction opposite the tilt of the frame).


```{r s2v summary stat table, echo=FALSE}
s2v_descriptives <- saccade_to_vert_magnitude %>% group_by(saccade_to_vert_magnitude[2]) %>%
  summarize(
    Mean = mean(frame_effect_v)
    , Median = median(frame_effect_v)
    , SD = sd(frame_effect_v)
    , Min = min(frame_effect_v)
    , Max = max(frame_effect_v)
  ) %>% 
  mutate(FRAME_SIZE_VAL = recode(FRAME_SIZE_VAL, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

s2v_descriptives <- s2v_descriptives %>% 
  rename("Frame Size"= FRAME_SIZE_VAL)
  
#p_descriptives[, -1] <- printnum(p_descriptives[, -1])

desc_v<-apa_table(
  s2v_descriptives
  , caption = "Saccade-to-Vertical Task"
  , escape = TRUE,
  added_stub_head = "Frame Size"
)
#names(desc_perc)[1]<- "Frame Size"

desc_v
```

```{r s2v ttest against zero, echo=FALSE}
s2v_ttest_df<-saccade_to_vert_magnitude %>% group_by(FRAME_SIZE_VAL) %>% do(tidy(t.test(.$frame_effect_v)))
s2v_ttest_table<-nice_table(s2v_ttest_df,
                            title= "Saccade-to-Vertical: Visuovestibular Effect")
```

```{r s2v ttest table}
s2v_ttest_df<-saccade_to_vert_magnitude %>% group_by(FRAME_SIZE_VAL) %>% do(tidy(t.test(.$frame_effect_v)))
nice_table(s2v_ttest_df)
```

```{r s2v aov frame size effect}
vv_mag_anova<- aov(frame_effect_v~FRAME_SIZE_VAL, data =saccade_to_vert_magnitude)
#summary(vv_mag_anova)
tukey_vv<-tukey_hsd(vv_mag_anova)
apa_table(tukey_vv)
```

```{r s2v graph, echo=FALSE}
set.seed(1)
saccade_to_vert_magnitude<- saccade_to_vert_magnitude %>% 
  ungroup()%>% 
  mutate(FRAME_SIZE_VAL = recode(FRAME_SIZE_VAL, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

vv_mag<- ggwithinstats(
  data = saccade_to_vert_magnitude,
  x = FRAME_SIZE_VAL,
  y = frame_effect_v,
  type = "parametric",
  xlab = "Frame Size",
  ylab = "Visuo-vestibular Effect",
  bf.message = FALSE,
  results.subtitle = FALSE,
  centrality.path = TRUE,
  centrality.label.args = list(size = 0,
  segment.linetype = 0, alpha = 0),
  ggsignif.args = list(textsize = 0))

#gginnards::delete_layers(vv_mag, "GeomText")

gginnards::delete_layers(vv_mag, "StatSummary")

#vv_mag



# s2v_bxplt<- ggboxplot(saccade_to_vert_magnitude, x = "FRAME_SIZE_VAL", y = "frame_effect_v")+
#   labs(x = "Frame Size", y = "Visuo-vestibular Effect")
# s2v_bxplt
```

```{r s2v perception correlation by frame graph 1, echo=FALSE}

s2v_2<- s2v_abs %>%
  ungroup() %>% 
  mutate(task = "s2v") %>% 
  rename(magnitude = frame_effect_v) %>%
  mutate((frame_size=recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large')))
  
s2v_2$frame_size <- s2v_2$`(...)`

colnames(s2v_2)<- c("sid", "frame_size", "magnitude", "task", "sub_1")

s2v_2<-s2v_2 %>%
  select(-sub_1)

perc_x_s2v_df<- rbind(s2v_2,perception_abs)

perc_x_s2v_df<- perc_x_s2v_df %>%
  pivot_wider(names_from = task, values_from = magnitude)

corr_perc_s2v<-cor.test(perc_x_s2v_df$perception,perc_x_s2v_df$s2v)  

ggplot(perc_x_s2v_df)+
  aes(perception, s2v, color = frame_size)+
  geom_point()+
  stat_smooth(method =lm, show.legend = FALSE)+
  facet_wrap(~frame_size, nrow =1)+
  theme(aspect.ratio = 1)+
#  ggtitle("Perception and Saccade to Vertical")+
  labs( x = "Perception", y = " Saccade to Vertical")

```


### Saccade to Rod : Orientation Contrast Effect

The effect of the frames was quantified by subtracting the mean errors for the counterclockwise-tilted frames from those of the clockwise-tilted frames then halving this value to get a measure of the average effect of a single frame (negative values indicated eye movements that deviated in the direction opposite the tilt of the frame).

```{r s2r summary stat table, echo=FALSE}
s2r_descriptives <- saccade_to_rod_magnitude %>% group_by(saccade_to_rod_magnitude[2]) %>%
  summarize(
    Mean = mean(frame_effect_r)
    , Median = median(frame_effect_r)
    , SD = sd(frame_effect_r)
    , Min = min(frame_effect_r)
    , Max = max(frame_effect_r)
  ) %>% 
  mutate(FRAME_SIZE_VAL = recode(FRAME_SIZE_VAL, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

s2r_descriptives <- s2r_descriptives %>% 
  rename("Frame Size"= FRAME_SIZE_VAL)
  
#p_descriptives[, -1] <- printnum(p_descriptives[, -1])

desc_r<-apa_table(
  s2r_descriptives
  , caption = "Saccade-to-Rod Task: Orientation Contrast Effect"
  , escape = TRUE,
  added_stub_head = "Frame Size"
)
#names(desc_perc)[1]<- "Frame Size"

desc_r
```

```{r s2r ttest table, echo = FALSE}
s2r_ttest_df<-saccade_to_rod_magnitude %>% group_by(FRAME_SIZE_VAL) %>% do(tidy(t.test(.$frame_effect_r)))
nice_table(s2r_ttest_df)
```

```{r s2r ttest, include = FALSE, echo = FALSE}

s2r_mag_175 <- saccade_to_rod_magnitude %>%
  filter(FRAME_SIZE_VAL== "175")
s2r_175_ttest <- t.test(s2r_mag_175$frame_effect_r)


s2r_mag_410 <- saccade_to_rod_magnitude %>%
  filter(FRAME_SIZE_VAL== "410")
s2r_410_ttest <- t.test(s2r_mag_410$frame_effect_r)

s2r_mag_645 <- saccade_to_rod_magnitude %>%
  filter(FRAME_SIZE_VAL== "645")
s2r_645_ttest <- t.test(s2r_mag_645$frame_effect_r)

s2r_mag_880 <- saccade_to_rod_magnitude %>%
  filter(FRAME_SIZE_VAL== "880")
s2r_880_ttest <- t.test(s2r_mag_880$frame_effect_r)

#Report Stats for each 

s2r_175<- report(s2r_175_ttest)
s2r_175

s2r_410<- report(s2r_410_ttest)
s2r_410

s2r_645 <- report(s2r_645_ttest)
s2r_645

s2r_880<- report(s2r_880_ttest)
s2r_880

```

```{r s2r within graph, echo=FALSE}

set.seed(1)
saccade_to_rod_magnitude<- saccade_to_rod_magnitude %>%
  mutate(frame_effect_r = -1*frame_effect_r) %>% 
  ungroup() %>% 
  mutate(FRAME_SIZE_VAL = recode(FRAME_SIZE_VAL, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

## 
oc_mag_anova<- aov(frame_effect_r~FRAME_SIZE_VAL, data =saccade_to_rod_magnitude)
summary(oc_mag_anova)
tukey_oc<-tukey_hsd(oc_mag_anova)
#summary(tukey_oc)
apa_table(tukey_oc)

oc_mag<-ggwithinstats(
  data = saccade_to_rod_magnitude,
  x = FRAME_SIZE_VAL,
  y = frame_effect_r,
  type = "parametric",
  xlab = "Frame Size",
  ylab = "Orientation Contrast Effect",
#  title = "Illusion Magnitude for Saccade-to-Rod Task",
  bf.message = FALSE,
  results.subtitle = FALSE,
  centrality.path = TRUE,
  centrality.label.args = list(size = 0, segment.linetype = 0, alpha = 0),
  ggsignif.args = list(textsize = 0))


#gginnards::delete_layers(oc_mag, "GeomText")

gginnards::delete_layers(oc_mag, "StatSummary")

#oc_mag
#extract_stats(oc_mag)


```

```{r perception s2r correlation by frame 1, echo=FALSE, fig.dim=c(1,4)}

s2r_2<- s2r_abs %>%
  mutate(frame_size = recode(sub_1, "175" = 'Small', "410"= 'Medium', "645"= 'Large', "880"= 'Extra Large')) %>% 
  mutate( task = "s2r") %>% 
  mutate("magnitude"= frame_effect_r) %>% 
  mutate("sid"= sub_2) %>% 
  select(sid,frame_size,magnitude,task)

s2r_2$sid <- substr(s2r_2$sid, start = 2, stop = 8) #clean subject ids


s2r_2$sid<-as_factor(s2r_2$sid)

perception_abs_2<-perception_abs %>% 
  mutate(frame_size = recode(frame_size , "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

perception_abs_2$sid<-as_factor(perception_abs_2$sid)
perception_abs_2$task<- as_factor(perception_abs_2$task)
perc_x_s2r_df<- rbind(s2r_2,perception_abs_2)

perc_x_s2r_df<- perc_x_s2r_df %>%
   pivot_wider(names_from = task, values_from = magnitude)

```

```{r perc by rod 1, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(perc_x_s2r_df)+
  aes(perception, s2r, color = frame_size)+
  geom_point(show.legend = FALSE)+
  stat_smooth(method = lm, show.legend = FALSE)+
  facet_grid(. ~ frame_size)+ 
  theme(aspect.ratio = 1)+
  labs(x= "Perception Task", y = "Saccade to Rod")

#  facet_wrap(~frame_size, nrow = 1)+
#  ggtitle("Perception and Saccade to Rod")+


```


### Combined Saccades and Perception Task Comparison

So far the perceptual and orientation contrast effect were reported as negative numbers, indicating that the perceptual response or saccade erred in the opposite direction of the tilt of the frame. However, it should be noted that for the purpose of making an additive comparison between summed saccade tasks and the perceptual response, we used the inverse value of the OC effect.

```{r summary stats combined, include=FALSE, echo=FALSE}
perc_x_sacc_df %>%
 group_by(frame_size,task) %>%
 get_summary_stats(magnitude, type = "mean_sd")

perc_x_sacc_desc<- nice_table(perc_x_sacc_df)

# perc_x_sacc_descriptives <- perc_x_sacc_df %>% group_by(frame_size,task) %>%
#   summarize(
#     Mean = mean(magnitude)
#     , Median = median(magnitude)
#     , SD = sd(magnitude)
#     , Min = min(magnitude)
#     , Max = max(magnitude)
#   ) %>% 
#   mutate(frame_size = recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))
# 
# perc_x_sacc_descriptives <- perc_x_sacc_descriptives %>% 
#   rename("Frame Size"= frame_size)
#   
# #p_descriptives[, -1] <- printnum(p_descriptives[, -1])
# 
# desc_p_x_sacc<-apa_table(
#   perc_x_sacc_descriptives
#   , caption = "Combined Saccade Tasks and Perception Tasks"
#   , escape = TRUE,
#   added_stub_head = "Frame Size"
# )
# #names(desc_perc)[1]<- "Frame Size"
# 
# desc_p_x_sacc
# ```
```  

```{r boxplot perception_x_saccade, echo=FALSE}
psd<- perc_x_sacc_df %>% 
  mutate(frame_size = recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

bxp<- ggpubr::ggboxplot(psd,x = "frame_size", y = "magnitude", color = "task")+
  ggtitle("Illusion Magnitude for Perception and Combined Saccade Tasks")+
  labs( x = "Frame Size", y = "Illusion Magnitude", color = "Task")+
  scale_color_discrete(name = "Task", labels = c("Combined Saccade Tasks", "Perception Task"))
bxp
```

```{r perception and combined saccade anova, echo = FALSE, include = FALSE}

perc_sacc_aov<- perc_x_sacc_df %>% 
  ungroup() %>%
  anova_test(dv= magnitude, wid= sid, within = c(frame_size,task))

get_anova_table(perc_sacc_aov)

```

```{r perception and saccade correlation graph, echo=FALSE}

corr_perc_sacc<-cor.test(across_frames$perception, across_frames$combined_saccade)  
report(corr_perc_sacc)  

ggplot(across_frames)+
  aes(perception, combined_saccade)+
  geom_point(aes(color=frame_size))+
  stat_smooth(method = lm)+
  labs(x = "Perceptual Effect", y ="Combined Visuovestibular and Orientation Contrast Effects" )
```

```{r combined sacc by perception cor, echo = FALSE}
across_frames<- perc_x_sacc_df %>%
  pivot_wider(names_from = task, values_from = magnitude)


#175
comb_sacc_perc_175<- across_frames %>% 
  filter(frame_size == "Small")

cor_comb_perc_175<- cor.test(comb_sacc_perc_175$perception,comb_sacc_perc_175$combined_saccade)
cor_comb_perc_175
#410
comb_sacc_perc_410<- across_frames %>% 
  filter(frame_size == "Medium")

cor_comb_perc_410<- cor.test(comb_sacc_perc_410$perception,comb_sacc_perc_410$combined_saccade)
cor_comb_perc_410
#645
comb_sacc_perc_645<- across_frames %>% 
  filter(frame_size == "Large")

cor_comb_perc_645<- cor.test(comb_sacc_perc_645$perception,comb_sacc_perc_645$combined_saccade)
cor_comb_perc_645
#880
comb_sacc_perc_880<- across_frames %>% 
  filter(frame_size == "Extra Large")

cor_comb_perc_880<- cor.test(comb_sacc_perc_880$perception,comb_sacc_perc_880$combined_saccade)
cor_comb_perc_880
```

```{r perception and saccade correlation by frame size, echo=FALSE}

corr_perc_sacc<-cor.test(across_frames$perception,across_frames$combined_saccade)  
report(corr_perc_sacc)  

ggplot(across_frames)+
  aes(perception, combined_saccade, color = frame_size)+
  geom_point(show.legend = FALSE)+
  stat_smooth(method=lm, show.legend =FALSE)+
  facet_wrap(~frame_size, nrow=1)+
#  ggtitle("Perception and Combined Saccade Tasks")+
  theme(aspect.ratio = 1)+
  labs(x = "Perception", y = "Combined Saccade Tasks")



```

**Perception and Saccade-to-Vertical**

```{r s2v perception correlation by frame graph, echo=FALSE}

s2v_2<- s2v_abs %>%
  ungroup() %>% 
  mutate(task = "s2v") %>% 
  rename(magnitude = frame_effect_v) %>%
  mutate((frame_size=recode(frame_size, "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large')))
  
s2v_2$frame_size <- s2v_2$`(...)`

colnames(s2v_2)<- c("sid", "frame_size", "magnitude", "task", "sub_1")

s2v_2<-s2v_2 %>%
  select(-sub_1)

perc_x_s2v_df<- rbind(s2v_2,perception_abs)

perc_x_s2v_df<- perc_x_s2v_df %>%
  pivot_wider(names_from = task, values_from = magnitude)

corr_perc_s2v<-cor.test(perc_x_s2v_df$perception,perc_x_s2v_df$s2v)  

ggplot(perc_x_s2v_df)+
  aes(perception, s2v, color = frame_size)+
  geom_point()+
  stat_smooth(method =lm, show.legend = FALSE)+
  facet_wrap(~frame_size, nrow =1)+
  theme(aspect.ratio = 1)+
#  ggtitle("Perception and Saccade to Vertical")+
  labs( x = "Perception", y = " Saccade to Vertical")

```

```{r, s2v perc corr tests, include= FALSE}
#175
s2v_perc_175<- perc_x_s2v_df %>% 
  filter(frame_size =="Small")

cor_s2v_perc_175<- cor.test(s2v_perc_175$perception,s2v_perc_175$s2v)
cor_s2v_perc_175

#410
s2v_perc_410<- perc_x_s2v_df %>% 
  filter(frame_size =="Medium")

cor_s2v_perc_410<- cor.test(s2v_perc_410$perception,s2v_perc_410$s2v)
cor_s2v_perc_410

#645
s2v_perc_645<- perc_x_s2v_df %>% 
  filter(frame_size == "Large")
cor_s2v_perc_645<- cor.test(s2v_perc_645$perception,s2v_perc_645$s2v)
cor_s2v_perc_645

#880
s2v_perc_880<- perc_x_s2v_df %>% 
  filter(frame_size == "Extra Large")

cor_s2v_perc_880<- cor.test(s2v_perc_880$perception,s2v_perc_880$s2v)
cor_s2v_perc_880
```

**Perception and Saccade-to-Rod**

```{r perception s2r correlation by frame, echo=FALSE, fig.dim=c(1,4)}
s2r_2<- s2r_abs %>%
  mutate(frame_size = recode(sub_1, "175" = 'Small', "410"= 'Medium', "645"= 'Large', "880"= 'Extra Large')) %>% 
  mutate( task = "s2r") %>% 
  mutate("magnitude"= frame_effect_r) %>% 
  mutate("sid"= sub_2) %>% 
  select(sid,frame_size,magnitude,task)

s2r_2$sid <- substr(s2r_2$sid, start = 2, stop = 8) #clean subject ids


s2r_2$sid<-as_factor(s2r_2$sid)

perception_abs_2<-perception_abs %>% 
  mutate(frame_size = recode(frame_size , "175" = 'Small', "410" = 'Medium', "645" = 'Large', "880" = 'Extra Large' ))

perception_abs_2$sid<-as_factor(perception_abs_2$sid)
perception_abs_2$task<- as_factor(perception_abs_2$task)
perc_x_s2r_df<- rbind(s2r_2,perception_abs_2)

perc_x_s2r_df<- perc_x_s2r_df %>%
   pivot_wider(names_from = task, values_from = magnitude)

```

```{r perc by rod, echo=FALSE}
ggplot(perc_x_s2r_df)+
  aes(perception, s2r, color = frame_size)+
  geom_point(show.legend = FALSE)+
  stat_smooth(method = lm, show.legend = FALSE)+
  facet_grid(. ~ frame_size)+ 
  theme(aspect.ratio = 1)+
  labs(x= "Perception Task", y = "Saccade to Rod")

#  facet_wrap(~frame_size, nrow = 1)+
#  ggtitle("Perception and Saccade to Rod")+


```

```{r perception and s2r corr for ind frame sizes, echo=FALSE, inlcude = FALSE}
#175
s2r_perc_175<- perc_x_s2r_df %>%
  filter(frame_size == "Small")

cor_s2r_perc_175<- cor.test(s2r_perc_175$perception,s2r_perc_175$s2r)
#report(cor_s2r_perc_175)
cor_s2r_perc_175

#410
s2r_perc_410<- perc_x_s2r_df %>%
  filter(frame_size == "Medium")

cor_s2r_perc_410<- cor.test(s2r_perc_410$perception,s2r_perc_410$s2r)
#report(cor_s2r_perc_410)
cor_s2r_perc_410
#645
s2r_perc_645<- perc_x_s2r_df %>%
  filter(frame_size =="Large")
cor_s2r_perc_645<- cor.test(s2r_perc_645$perception,s2r_perc_645$s2r)
#report(cor_s2r_perc_645)
cor_s2r_perc_645

#880
s2r_perc_880<- perc_x_s2r_df %>%
  filter(frame_size == "Extra Large")

cor_s2r_perc_880<- cor.test(s2r_perc_880$perception,s2r_perc_880$s2r)
#report(cor_s2r_perc_880)
cor_s2r_perc_880


```
### Task by Frame Size
```{r task by frame size aov, include=FALSE, echo=FALSE}
task_by_frame<- all_task %>% 
  select(sid, frame_size, vv, oc)
task_by_frame$sid<-as_factor(task_by_frame$sid)
task_by_frame$oc<-task_by_frame$oc*-1

task_by_frame_long<- task_by_frame%>% 
  pivot_longer(
    cols = c(vv,oc),
    names_to = "task",
    values_to = "magnitude"
  )

task_by_frame_long$task<- as_factor(task_by_frame_long$task)
```

```{r task by fram aov and summary stats}

#two way anova task X frame size summary stats

task_by_frame_long %>% 
  group_by(frame_size,task) %>% 
  get_summary_stats(magnitude,type = "mean_sd")

#box plot 
task_frame_bxp<- ggboxplot(
  task_by_frame_long, x = "frame_size", y = "magnitude", color = "task", pallet ="jco")

task_frame_bxp  

```


### Model Comparison

For each frame size a hierarchical design was employed using two models: 1) model 1 predicted the overall RFI magnitude  (measured by the perception task) from the visuovestibular effect (measured by the saccade-to-vertical task) and  2) model 2 predicted the overall RFI magnitude from visuovestibular effect and the orientation contrast effect (measured by the saccade-to-rod task). 

#### Small Frame

```{r model comparison small frame, echo = FALSE}
all_task<- all_task %>%
  mutate( oc = -1*oc)


df_small<- all_task %>% 
  filter(frame_size == "175")

df_175_across<- df_small %>% 
  select(-sid, -frame_size)

#ggpairs(df_175_across)
model_1_small<- lm(perc~vv, df_small)
summary(model_1_small)

model_2_small<- lm(perc~ vv +oc, df_small)
summary(model_2_small)

#change in r squared
small_rsq_change<- summary(model_2_small)$r.squared - summary(model_1_small)$r.squared
small_rsq_change

aov_small<- anova(model_1_small,model_2_small, test = "F")
aov_small

small_frame_models<- list("Model 1" = model_1_small,
                          "Model 2" = model_2_small)

modelsummary(small_frame_models)

```

####Medium Frame

```{r model comparison frame 410, echo = FALSE}

df_medium<- all_task %>% 
  filter(frame_size == "410")

df_410_across<- df_medium %>% 
  select(-sid, -frame_size)

#ggpairs(df_410_across)


model_1_medium<- lm(perc~vv, df_medium)
summary(model_1_medium)

model_2_medium<- lm(perc~ vv +oc, df_medium)
summary(model_2_medium)

#change in r squared
medium_rsq_change<- summary(model_2_medium)$r.squared - summary(model_1_medium)$r.squared
medium_rsq_change

aov_medium<- anova(model_1_medium,model_2_medium, test = "F")
aov_medium

medium_frame_models<- list("Model 1" = model_1_medium,
                          "Model 2" = model_2_medium)
modelsummary(medium_frame_models)
```

####Large Frame

```{r model comparison frame large, echo= FALSE}

df_large<- all_task %>% 
  filter(frame_size == "645")

df_large_across<- df_large %>% 
  select(-sid, -frame_size)

#ggpairs(df_410_across)


model_1_large<- lm(perc~vv, df_large)
summary(model_1_large)

model_2_large<- lm(perc~ vv +oc, df_large)
summary(model_2_large)
#change in r squared
large_rsq_change<- summary(model_2_large)$r.squared - summary(model_1_large)$r.squared
large_rsq_change


aov_large<- anova(model_1_large,model_2_large, test = "F")
aov_large

large_frame_models<- list("Model 1" = model_1_large,
                          "Model 2" = model_2_large)
modelsummary(large_frame_models)
```

####Extra Large Frame

```{r model comparison frame 880, echo = FALSE}

df_xl<- all_task %>% 
  filter(frame_size == "880")

df_xl_across<- df_xl %>% 
  select(-sid, -frame_size)

#ggpairs(df_880_across)

model_1_xl<- lm(perc~vv, df_xl)
summary(model_1_xl)
model_2_xl<- lm(perc~ vv +oc, df_xl)
summary(model_2_xl)
#change in r squared
xl_rsq_change<- summary(model_2_xl)$r.squared - summary(model_1_xl)$r.squared
xl_rsq_change

aov_xl<- anova(model_1_xl,model_2_xl, test = "F")
aov_xl

xl_frame_models<- list("Model 1" = model_1_xl,
                          "Model 2" = model_2_xl)
modelsummary(xl_frame_models)
```


### {-}